Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-01 pirouette_supplement.tex
Add 'edit.sh', text in 'subsec:distribution' is 80 chars per line max
Interpret section 8.14, progress #98

\new{
The resulting error distributions are showed in Fig. \ref{fig:replicate_trees}. We present results for cases where (1) the generative model has been used or (2) the model with highest evidence has been selected for the inference.
From the plots we can see that in both cases there is a clear distinction between the two distributions (true and twin), suggesting that the inference models that have been used cannot capture in an accurate way the features of the diversity-dependent tree prior used to simulate the original trees. 
}

@@

>>>>

\new{
  The resulting error distributions are shown in Fig. \ref{fig:replicate_trees}. 
  We present results for cases where (1) the generative model has been used 
  or (2) the model with highest evidence has been selected for the inference.
  From the plots we can see that in both cases there is a clear distinction 
  between the two distributions (true and twin), suggesting that the inference 
  models that have been used cannot capture in an accurate way the features of 
  the diversity-dependent tree prior used to simulate the original trees. 
}

@@

\new{
  We can observe that the error increases for mutation rates above
  `1.0 / crown age`. Below this value, the errors are the same.
  For these lower mutation rates, however, the shape of the error
  distribution changes for the baseline/generative models,
  deviating more and more from the gamma-distribution-like shape
  as is stil present in the twin distributions.
}
